\vspace{-2cm}Formation Control of AAUSHIP

### 2015-11-14 paper.tex
Add figure with obstacle objects

>>>>

Running the same setup as used in figure~\vref{fig:potform}, but with the addition of some objects in the way of the paths it can be seen how the ships tries to evade the obstacles. The obstacles potential field is drawn as black circles. It shall be noted the plotted boundray is not a hard boundry, but only shows the radius whereby the potential field of the obstacles can affect other objects.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{fig/lawn-bar-formation-po}
  \caption{Same setups as in figure~\vref{fig:potform}, but with obstables positioned on the pathways.}
  \label{fig:potform-po}
\end{figure}
